### 2022-07-23 main.tex

\newcommand{\jd}[1]{\comment{cyan}{JD}{#1}}
\newcommand{\swp}[1]{\comment{magenta}{SWP}{#1}}
\newcommand{\bmb}[1]{\comment{blue}{BMB}{#1}}
\newcommand{\djde}[1]{\comment{red}{DJDE}{#1}}

@@

Asymptomatic infections have hampered the ability to characterize and prevent the transmission of SARS-CoV-2 throughout the ongoing pandemic.
Even though asymptomatic infections reduce the severity at the individual level, they can still make population-level outcomes worse by transmitting to others unknowingly.
Here, we show that intermediate levels of asymptomatic infection lead to the highest levels of epidemic fatalities in the presence of a strong reduction in symptomatic transmission rates, which can be caused by either behavioral changes or mitigation efforts.
We further generalize this result to show that intermediate levels of non-symptomatic transmission (including both presymptomatic and asymptomatic transmission) can also lead to the highest levels of fatalities.
Finally, we extend our framework to illustrate the importance of immunity profile in determining epidemic trajectories of future variants.

>>>>

\newcommand{\jd}[1]{\comment{cyan}{JD}{#1}}
\newcommand{\swp}[1]{\comment{magenta}{SWP}{#1}}
\newcommand{\weitz}[1]{\comment{blue}{WEITZ}{#1}}

@@

Asymptomatic infections have hampered the ability to characterize and prevent the transmission of SARS-CoV-2 throughout the ongoing pandemic.
Even though asymptomatic infections reduce severity at the individual level, they can still make population-level outcomes worse if asymptomatic individuals transmit more because they are unaware that they are infected.
Here, we show that intermediate levels of asymptomatic infection lead to the highest levels of epidemic fatalities when this increase in transmission, due either to individual behavior or mitigation efforts, is strong. 
We generalize this result to include presymptomatic transmission, and show that in this case as well intermediate levels of non-symptomatic transmission can lead to the highest levels of fatalities.
Finally, we extend our framework to illustrate the importance of immunity profile in determining epidemic trajectories of future variants.
